---
title: "PartB CA4"
author: "Conor Crean"
date: "`r Sys.Date()`"
<<<<<<< HEAD
output:
  html_document:
    theme: readable
    toc: yes
    toc_float: yes
=======
output: html_document
>>>>>>> 9e34d0450f37f6a35fcb5998ab5d7c42a6d70676
 
---
* #### **Table Of Contents:**

<<<<<<< HEAD
##### *Assumptions:*
* *Linear Regression Analysis*
* *Data Overview*
* *Histograms*
* *Checking Correlation coefficient of two variables*
* *Plotting data and creating linear regress model*
* *GGPlot of age and average monthly hours gaming*


# **Assumptions**
=======


#Assumptions
>>>>>>> 9e34d0450f37f6a35fcb5998ab5d7c42a6d70676
The variables chosen include age and the average monthly hours of gaming.
My assumption that as players age the less hours that they can dedicated to playing video games due to work and other commitments.



<<<<<<< HEAD
### **Linear Regression Analysis**

```{r , echo=FALSE, include=FALSE}
=======
#Linear Regression Analysis
##### *Data Overview*
```{r , echo=FALSE}
>>>>>>> 9e34d0450f37f6a35fcb5998ab5d7c42a6d70676
#Library for graphs and data presentation loaded
library(readr)
library(tidyverse)
library(ggplot2)


#data assigned to a variable
daie_ca4_game_data <- read_csv("amalgamated_game_survey_250_2022.csv")
```

### **Data Overview**
```{r echo=FALSE, , echo=FALSE}
#Data checked head and tails along with summary
#View(daie_ca4_game_data)
head(daie_ca4_game_data,5)
tail(daie_ca4_game_data,5)
summary(daie_ca4_game_data)




```

<<<<<<< HEAD
### **Histograms**
=======
#Histograms
>>>>>>> 9e34d0450f37f6a35fcb5998ab5d7c42a6d70676
```{r , echo=FALSE}
library('statsr')

hist(daie_ca4_game_data$age )
hist(daie_ca4_game_data$avg_monthly_expenditure_dlc  )
```


<<<<<<< HEAD

### **Checking Correlation coefficient of two variables**
=======
Variables:
gender
age
top_reason_gaming
gaming_platform
favourite_game
avg_monthly_hrs_gaming 
avg_years_playing_games
avg_monthly_expenditure_dlc
ethnicity
play_roblox
use_steam



#Checking Corralation cooefficent of two variables
>>>>>>> 9e34d0450f37f6a35fcb5998ab5d7c42a6d70676
```{r , echo=FALSE}
cor(daie_ca4_game_data$age, daie_ca4_game_data$avg_monthly_hrs_gaming)
cor(daie_ca4_game_data$age, daie_ca4_game_data$avg_years_playing_games)
cor(daie_ca4_game_data$age, daie_ca4_game_data$avg_monthly_expenditure_dlc)

cor(daie_ca4_game_data$avg_monthly_hrs_gaming, daie_ca4_game_data$avg_years_playing_games)
cor(daie_ca4_game_data$avg_monthly_hrs_gaming, daie_ca4_game_data$avg_monthly_expenditure_dlc)



    
```



<<<<<<< HEAD
### **Plotting data and creating linear regress model.**
=======
#Plotting data and creating linear regress model.
>>>>>>> 9e34d0450f37f6a35fcb5998ab5d7c42a6d70676
```{r , echo=FALSE}
plot_ss(age, avg_monthly_hrs_gaming, daie_ca4_game_data)

m1 <- lm(age ~ avg_monthly_hrs_gaming, data = daie_ca4_game_data)
summary(m1)


plot(daie_ca4_game_data$age ~ daie_ca4_game_data$avg_monthly_hrs_gaming)
abline(m1)


plot(m1$residuals ~ daie_ca4_game_data$avg_monthly_hrs_gaming)
abline(h = 0, lty = 3)  # adds a horizontal dashed line at y = 0

hist(m1$residuals)


qqnorm(m1$residuals)
qqline(m1$residuals)
```

<<<<<<< HEAD
### **GGPlot of age and average monthly hours gaming**
=======
#GGPlot of age and average monthly hours gaming
>>>>>>> 9e34d0450f37f6a35fcb5998ab5d7c42a6d70676
```{r , echo=FALSE}
ggplot(daie_ca4_game_data,aes(age, avg_monthly_hrs_gaming)) +
  geom_point() +
  geom_smooth(method='lm')


```
