---
title: "PartB CA4"
author: "Conor Crean"
date: "`r Sys.Date()`"
output: html_document
 
---



#Assumptions
The variables chosen include age and the average monthly hours of gaming.
My assumption that as players age the less hours that they can dedicated to playing video games due to work and other commitments.



#Linear Regression Analysis
##### *Data Overview*
```{r , echo=FALSE}
#Library for graphs and data presentation loaded
library(readr)
library(tidyverse)
library(ggplot2)


#data assigned to a variable
daie_ca4_game_data <- read_csv("amalgamated_game_survey_250_2022.csv")


#Data checked head and tails along with summary
#View(daie_ca4_game_data)
head(daie_ca4_game_data,5)
tail(daie_ca4_game_data,5)
summary(daie_ca4_game_data)




```

#Histograms
```{r , echo=FALSE}
library('statsr')

hist(daie_ca4_game_data$age )
hist(daie_ca4_game_data$avg_monthly_expenditure_dlc  )
```


Variables:
gender
age
top_reason_gaming
gaming_platform
favourite_game
avg_monthly_hrs_gaming 
avg_years_playing_games
avg_monthly_expenditure_dlc
ethnicity
play_roblox
use_steam



#Checking Corralation cooefficent of two variables
```{r , echo=FALSE}
cor(daie_ca4_game_data$age, daie_ca4_game_data$avg_monthly_hrs_gaming)
cor(daie_ca4_game_data$age, daie_ca4_game_data$avg_years_playing_games)
cor(daie_ca4_game_data$age, daie_ca4_game_data$avg_monthly_expenditure_dlc)

cor(daie_ca4_game_data$avg_monthly_hrs_gaming, daie_ca4_game_data$avg_years_playing_games)
cor(daie_ca4_game_data$avg_monthly_hrs_gaming, daie_ca4_game_data$avg_monthly_expenditure_dlc)



    
```



#Plotting data and creating linear regress model.
```{r , echo=FALSE}
plot_ss(age, avg_monthly_hrs_gaming, daie_ca4_game_data)

m1 <- lm(age ~ avg_monthly_hrs_gaming, data = daie_ca4_game_data)
summary(m1)


plot(daie_ca4_game_data$age ~ daie_ca4_game_data$avg_monthly_hrs_gaming)
abline(m1)


plot(m1$residuals ~ daie_ca4_game_data$avg_monthly_hrs_gaming)
abline(h = 0, lty = 3)  # adds a horizontal dashed line at y = 0

hist(m1$residuals)


qqnorm(m1$residuals)
qqline(m1$residuals)
```

#GGPlot of age and average monthly hours gaming
```{r , echo=FALSE}
ggplot(daie_ca4_game_data,aes(age, avg_monthly_hrs_gaming)) +
  geom_point() +
  geom_smooth(method='lm')


```
